InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-27 paper.tex
Added two sections about image detection models

A similar model, but in a more recent version is the GPT-4 model. The model is yet to be released by it's developer OpenAI, but is available through an API. Compared to its predecessors GPT-4 is a multimodal model, which is not only capable of using text for input but also images. The model is trained on Next-Token-Prediction and is capable and was post-training aligned to better adhere to desired behaviour. The model is capable to perform well in different professional benchmarks out of a variety of domains and can demonstrate it's performance in different languages. \cite{openai2023gpt4}

@@

>>>>

@@

Another AI generated image detector model is \textbf{Is It AI?} developed by Is It AI. The tool first determines different features of the image, e.g. colour patterns, shapes and textures. These features are determined using machine learning models. Afterwards, the patterns are compared to those, typically contained in human- or AI-generated content. The Is It AI-model was trained on large datasets of human- and AI-generated content to receive the base patterns to compare to. \cite{IsItAI2024}

There is also an AI-generated-image-detection-approach from Content at Scale. They published their \textbf{Advanced AI Image Detector} as a web tool to detect generated AI images. The application categorizes the input content by evaluating pixels, smoothness and other AI image patterns. \cite{ContentAtScale2024Advanced}
